Tor's Usability for Censorship Circumvention

### 2016-04-04 pets2017-paper/pets2017-paper.tex
Include time_to_success and time_to_success_clamped figures.

\subsection{Results} 
{\color {red} This will be the main part of the paper--where we report on the data that we collected through the xlab experiment. Some of the questions we want to answer are: did the new interface improve success rate? did the new interface only help certain people? Did people take longer or shorter in the new version? Did we shift participants' behaviors in the new interface? Are the way people approach trying different configurations affected? are there existing problems for both interfaces? (we know for sure that users still not receiving feedback is an issue. I don't know how many of our participants actually saw our helpful error messages, since they took minutes to pop up, and some never pop up at all..)}

>>>>

\subsection{Results}

\begin{figure}
\centering
\includegraphics{time_to_success}
\caption{
Time to first success, by censorship environment and interface.
The dots show the raw completion times;
while the boxplots show the medians and interquartile ranges.
}
\end{figure}

\begin{figure}
\centering
\includegraphics{time_to_success_clamped}
\caption{
Time to first success, by censorship environment and interface.
Here, non-finishing participants are assigned a time of 40 minutes.
}
\end{figure}

{\color {red} This will be the main part of the paper--where we report on the data that we collected through the xlab experiment. Some of the questions we want to answer are: did the new interface improve success rate? did the new interface only help certain people? Did people take longer or shorter in the new version? Did we shift participants' behaviors in the new interface? Are the way people approach trying different configurations affected? are there existing problems for both interfaces? (we know for sure that users still not receiving feedback is an issue. I don't know how many of our participants actually saw our helpful error messages, since they took minutes to pop up, and some never pop up at all..)}
